---
title: "Test"
author: "Mark D."
date: "6 March 2018"
output: 
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r process_data}
# Week 1 activity
# lines starting with a '#' are comments

# import the csv data.
resp <- read.csv(here::here("01-CTT", "Bscored.csv"), stringsAsFactors = FALSE)

# calculate the score for each student (each row)
score <- apply(resp, 1, sum, na.rm = TRUE)

# calculate the item difficulty (each column)
itemdiff <- apply(resp, 2, mean, na.rm = TRUE) / apply(resp, 2, max, na.rm = TRUE)

# correlate each item column with the total score
disc <- apply(resp, 2, function(x) { cor(x, score - x, use = "complete.obs")})

```


##Introduction
This is a test of *English as Second Language* for Grade 7 students. This is a pilot test for the purpose of evaluating test items for their psychometric properties so that a final test form can be constructed based on the results of this pilot test. 

In total, `r nrow(resp)` students took the test. 

<!--- These are for html output file --->
<style type="text/css">
.table {
    width: 40%;
}
</style>
<center>


##Classical Test Theory Item Statistics
```{r results = 'asis', warning=FALSE}
discA <- as.integer(disc*100+0.5)  #these lines are for adding "*" and fixing two decimal places.
discB <- round(disc,2)
discB[(discA%%10)==0] <- paste(discB[(discA%%10)==0],"0",sep='')
discB[disc<0.2] <- paste("*",discB[disc<0.2],sep='')
itemstats <- data.frame(round(itemdiff,2),discB)
colnames(itemstats) <- c("Difficulty (%correct)","Discrimination(CTT)")
```
##Item difficulty and discrimination 
```{r comment=NA, warning=FALSE}
#itemstats
knitr::kable(itemstats,align = 'cc')

```


##Plot of Item 7 score and total score
```{r comment=NA, warning=FALSE}
plot(score-resp[,7],resp[,7], xlab="test score",ylab = "item 7")
```


